### 2018-05-18 manuscript.rmd
update wording

specimen_data_reduced<-as.data.frame(specimen_data_reduced)
xtable_specimen<-xtable(specimen_data_reduced,auto=TRUE, caption="A complete list of specimens used in this work, information from already published datasets added where available. New data indicated by Y, blank fields indicate that data were already published. For the species not on SRA, a link to the data is included in supplementary file 1.")
print(xtable_specimen,comment=F, include.rownames=FALSE, scalebox='0.7')

@@

We reconstruct palpons as present in the common ancestor of siphonophores (Fig. \@ref(reconstruct)B, \@ref(fig:BI-palp)), retained in most species, but lost three times independently in the branches leading to *Bargmannia* and *Rudjakovia* sp., in calycophorans, and in *Marrus claudanielis* and Undescribed sp. L. It remains to be clarified if small buds associated with nectophores within the nectosome of *Bargmannia* species (Dunn 2005) actually correspond to reduced palpons. The pyrostephid *Pyrostephos vanhoeffeni* (not sampled) has modified tentacle-less palpons (termed oleocysts), but the relationship between this species and *Rudjakovia* sp. is not known, so the exact patterns of loss within *Pyrostephidae* (here provisionally including *Rudjakovia* sp.) remain unclear. Within the calycophorans, one species *Stephanophyes superba* (not included in this phylogeny) has polyp-like zooids that have been described as palpons [@totton1965synopsis], but the exact identity of this zooid is not clear and needs further morphological examination.

>>>>

specimen_data_reduced<-as.data.frame(specimen_data_reduced)
xtable_specimen<-xtable(specimen_data_reduced,auto=TRUE, caption="A complete list of specimens used in this work, information from already published datasets added where available. New data indicated by Y, blank fields indicate that data were already published. For the species not on SRA, a link to the data is included in supplementary data 1.")
print(xtable_specimen,comment=F, include.rownames=FALSE, scalebox='0.7')

@@

We reconstruct palpons as present in the common ancestor of siphonophores (Fig. \@ref(reconstruct)B, \@ref(fig:BI-palp)), retained in most species, but lost three times independently in the branches leading to *Bargmannia* and *Rudjakovia* sp., in calycophorans, and in *Marrus claudanielis* and Undescribed sp. L. It remains to be clarified if small buds associated with nectophores within the nectosome of *Bargmannia* species [@Dunn:2005fv] actually correspond to reduced palpons. The pyrostephid *Pyrostephos vanhoeffeni* (not sampled) has modified tentacle-less palpons (termed oleocysts), but the relationship between this species and *Rudjakovia* sp. is not known, so the exact patterns of loss within *Pyrostephidae* (here provisionally including *Rudjakovia* sp.) remain unclear. Within the calycophorans, one species *Stephanophyes superba* (not included in this phylogeny) has polyp-like zooids that have been described as palpons [@totton1965synopsis], but the exact identity of this zooid is not clear and needs further morphological examination.
